---
title: "1 - Installing teachR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pkgdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__This page describes the installation process of [`teachR`](https://github.com/swarm-lab/teachR).__ 

`teachR` has not been released on [CRAN](https://cran.r-project.org/) yet, but it 
can be easily installed from its [GitHub repository](https://github.com/swarm-lab/teachR)
with the following steps. 

---

+ [1.1 - Before installing ](#before-installing)
+ [1.2 - Installing teachR](#installing-teachr)
+ [1.3 - Loading teachR](#loading-teachr)
  
---

## 1.1 - Before installing

Before installing `teachR`, you will need to install the latest version of the [`devtools`](https://CRAN.R-project.org/package=devtools) package. You can install [`devtools`](https://CRAN.R-project.org/package=devtools)  from 
[`CRAN`](https://cran.r-project.org) as follows: 

```{r, message=FALSE, eval=FALSE}
if (!require(devtools))
  install.packages("devtools")
```

---

## 1.2 - Installing teachR

You can install `teachR` as follows:

```{r, message=FALSE, eval=FALSE}
devtools::install_github("swarm-lab/teachR")
```

---

## 1.3 - Loading teachR

```{r, message=FALSE, eval=FALSE}
library(teachR)
```
